\documentclass{tccv_AH}
\usepackage[english]{babel}

\begin{document}
\sffamily

\part{Adin Horovitz}

%       CONTACT INFO

\personal
% Include GitHub here!
    [github.com/ahorovit]
    {24 Kent Place Apt 4 \newline Menlo Park, CA 94025}
    {(612) 229-2763}
    {ahorovit@gmail.com}
    {bit.ly/28iETw1}
%    {https://www.linkedin.com/in/adin-horovitz-85ab1b3}


%       EDUCATION
\vspace{-1em}

\section{Education}

\begin{yearlist}

\item[Boston University - Boston, MA]{2016}
     {MS, Computer Engineering - GPA 3.9}

\end{yearlist}

%       Courses -- Break up Yearlist to make this work

\vspace{-2em}
\begin{itemize}
    \itemsep-0.25em
    \itemindent2.5em
    \item{Introduction to Embedded Systems}
    \item{Computer Architecture}
    \item{Introduction to Logic Design}
    \item{VLSI Digital Circuit Design}
    \item{Applied Algorithms for Engineers}
    \item{Advanced Data Structures}
    \item{High Performance Computing}
    \item{Cybersecurity}

\end{itemize}

\begin{yearlist}

\item[Knox College - Galesburg, IL]{2008}
     {BA, Chemistry/Neuroscience - GPA 3.6}

\end{yearlist}





%       Programming Skills
\vspace{-1.75em}
\section{Software Skills \footnotesize{(Decreasing Order)}}

\begin{factlist}

\item{Languages}
     {C, C++, Java, MATLAB, R, Python, C\#, HTML, CSS, MIPS/x86 Assembly, SQL, \LaTeX}

\item{General}
     {Linux Kernel Module, Qt UI, Web Design (Visual Studio), GPU (CUDA), Arduino, Android App Dev (Android Studio), 
     Agile Project Management, Multicore (OpenMP/Pthreads), Shell scripting, QEMU, Verilog, Cadence Virtuoso, gdb, Git, IDA Pro}

\end{factlist}


%           Employment History
\vspace{-1.5em}
\section{Professional Experience}

\jobitem{Feb 2014 - Jul 2014}{Walden University School of Nursing}{Field Education Temp}
\begin{itemize}
    \itemsep-0.25em
    \item{Application process automation using R}
\end{itemize}

\medskip

\jobitem{Oct 2012 - Aug 2013}{Kaplan Test Preparation}{MCAT Instructor/Tutor}
%\begin{itemize}
%    \itemsep-0.25em
%    \item{Teach MCAT content and strategy to groups and individuals}
%    \item{Present course products at marketing events}
%\end{itemize}

\medskip

\jobitem{Aug 2009 - Aug 2012}{Lab of Neuropsychology, NIMH}{Animal Biologist}
\begin{itemize}
    \itemsep-0.25em
    \item{Exploratory data analysis using MATLAB}
    \item{Design/execute behavioral experiments}
    \item{Present findings in PowerPoint and poster formats}
\end{itemize}


\vfill
%\columnbreak



%       PROJECTS
\section{Selected Projects}

\begin{eventlist}

\item{2016}
     {Project Lead}
     {"bitQuit" -- IoT Smoking Abatement Tool}

The bitQuit is a smart cigarette case (and Android app) that helps smokers limit and track cigarette use. The case locks for a programmable interval, and custom switches count cigarettes remaining. These data are transmitted via BLE to the app, where smoking history and remaining wait time are viewable.

\item{2016}
     {Front-End, Firmware Developer}
     {"Display-o-Matic" e-Paper Tie}
     
This novelty tie has a built-in e-paper screen which displays arbitrary patterns/images. The user selects image thumbnail on touchscreen linked to Gumstix Verdex board. Selection is conveyed via Bluetooth to Raspberry Pi, which updates display via GPIO pins.



\item{2016}
     {CUDA Developer}
     {High Performance FFT}

Using a naive FFT as a baseline, high-performance methods (code motion, loop unrolling, OpenMP) were applied in various combinations to achieve a range of speedup. Also wrote a CUDA implementation to utilize GPU parallelism.

\item{2015}
     {Back-End Developer}
     {"JAMs" Playlist Application}

This Java-based playlist app maintains a database of playlists/songs based on popularity. Searches feature fast autocomplete using a Prefix Tree, and popularity ranking is maintained with a modified BST. UI implemented with JavaFX.


\item{2015}
     {Researcher}
     {C Vulnerability Static Analysis Tool}

Inspired by usr/bin/rsh vulnerability allowing addition of user to sudoers, this tool batch scans source code for privilege escalation risks. Python web scraper was used to download OS X source code in bulk.


\item{2014}
     {Lead Developer}
     {"LEAP Legends" -- Android App}

Original hexagon-based game for Android. Board elements and game pieces are implemented with OOP principles to create a simple, yet deep two-player strategy experience. 

\end{eventlist}




\end{document}
