
\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{paralist}
\linespread{0.98}
\definecolor{mygrey}{gray}{0.80}
\setlength{\parskip}{0cm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\usepackage[margin=0.5in]{geometry}
% Adjust margins to 0.5in on all sides
%\addtolength{\oddsidemargin}{-0.25in}
%\addtolength{\evensidemargin}{0.15in}
%\addtolength{\textwidth}{1.0in}
%\addtolength{\topmargin}{-0.5in}
%\addtolength{\textheight}{1.0in}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{\textit{Page \thepage \ of 2}}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Adin I. Horovitz}  & 612.229.2763 \\
24 Kent Place Apt 4 &  ahorovit@gmail.com \\
Menlo Park, CA  94025\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
  \ressubheading{Boston University}{Boston, MA}{Master of Science in Computer Engineering}{2014-2016}
  \begin{itemize}
    \resitem{Specialization in Software Engineering}{}
    \resitem{Graduate GPA: 3.93}{}
    \resitem{LEAP Scholar (Awarded half-tuition scholarship)}{}
  \end{itemize}

\item
  \ressubheading{Knox College}{Galesburg, IL}{Bachelor of Arts in Chemistry and Neuroscience}{2004-2008}
  \begin{itemize}
    \resitem{Graduated Cum Laude, GPA: 3.6}{}
  \end{itemize}
\end{itemize}


\resheading{Skills \& Extracurriculars}

\begin{description}
\item[\hspace{.025\textwidth}Languages:] 
\hfill \break
\textit{Advanced Experience -} C/C++, Java, MATLAB, R, Verilog\\
\textit{Basic Exposure -} C\#, Python, MIPS/x86 Assembly, SQL, HTML/CSS/ASP.NET, Shell Scripting, \LaTeX
%########################################
\item[\hspace{.025\textwidth}Additional Software Experience:]
Netbeans/Eclipse/Android Studio app development, Visual Studio 2015, Qt UI design, Cadence Virtuoso, Web Parameter/SQL injection, shell injection, gdb, IDA Pro
%########################################
\item[\hspace{.025\textwidth}Current Organizations/Recent Event Participation:]
BUILDs, SAGE, Boston Hacks Hackathon, Lincoln Laboratory's Weekly Modern Binary Exploitation Workshops
\end{description}




%######################################## PROFESSIONAL EXP

\resheading{Professional Experience}
\begin{itemize}

\item
\ressubheading{Walden University}{Minneapolis, MN}{Field Education Administrative Assistant}{February 2014 - July 2014}
\begin{itemize}
\resitem{Designed R software for automated application processing}
\resitem{Provided application database support for Nurse Practitioner (NP) course instructors}
\resitem{Processed practicum applications and provided feedback for NP students}
\resitem{Trained new staff}
\end{itemize}

\item
\ressubheading{Kaplan Test Prep}{Minneapolis, MN}{MCAT Course Instructor and Tutor}{October 2012 - August 2013}
\begin{itemize}
\resitem{Taught MCAT content and strategies to individuals and groups}
\resitem{Provided individualized feedback to students}
\resitem{Presented MCAT course products at marketing events}
\resitem{Communicated with administration in online work environment}
\end{itemize}

\item
\ressubheading{Laboratory of Neuropsychology, NIMH}{Bethesda, MD}{Animal Biologist}{August 2011 - August 2012}
\begin{itemize}
\resitem{Analyzed behavioral data using MATLAB and R analysis systems}
\resitem{Implemented system for simultaneous cortical transfusions of viral vector, reduced surgical duration}
\resitem{Designed/executed experiments visual sensory performance and motor coordination in Rhesus monkeys}
\resitem{Assisted in aseptic surgery on Rhesus monkeys and monitored post-operative health}
\resitem{Coauthored manuscripts in preparation for submission to peer-reviewed journals}
\resitem{Maintained records of experimentation and animal care}
\end{itemize}

\newpage

\ressubheading{}{}{Fellow, Intramural Research Training Award}{August 2009 - August 2011}
\begin{itemize}
\resitem{Analyzed behavioral and electrophysiological data using MATLAB}
\resitem{designing/executing studies examining visual working memory in Rhesus monkeys}
\resitem{Designed/executed experiments visual sensory performance and motor coordination in Rhesus monkeys}
\resitem{Developed and performed independent/complementary experiments}
\resitem{Monitored monkey health during/between electrophysiology experiments}
\resitem{Presented results in PowerPoint and poster formats}
\end{itemize}

\end{itemize}
%######################################  PROJECT EXP:
%\newpage

\resheading{Academic Projects}
\begin{itemize}

\item
\ressubheading{Android App - LEAP Legends}{}{Lead Developer}{September 2014 - December 2014}
\begin{itemize}
\resitem{Designed original hex-based game for Android. Wrote Java code for back-end game mechanics, and front-end user interaction.}
\end{itemize}

%-------------------------------JAMs Playlist
\item
\ressubheading{"JAMs" Playlist Application}{}{Lead Developer}{September 2015 - December 2015}
\begin{itemize}
\resitem{Headed team of three Advanced Data Structures students in building Java-based playlist management app. Wrote back-end code for searching (with autocomplete) and updating database of playlists/songs. Implemented Prefix Tree and modified BST for optimized performance. Helped design front-end with JavaFX.}
\end{itemize}

%-------------------------------Cyber Proj
\item
\ressubheading{Mac OS X - rsh/libmalloc Privilege Escalation Security Exploit}{}{Researcher}{October 2015 - December 2015}
\begin{itemize}
\resitem{Participated in a project researching recent lapse in the /usr/bin/rsh program on Mac OS X. An exploit was discovered where an unprivileged user was able to use the tool to open a rootshell via sudo. Implemented a web scraper for all of the OS X default program source code and developed a tool to analyze control flow and assess risk.}
\end{itemize}

%-------------------------------IoT QuitBit
\item
\ressubheading{"bitQuit" -- IoT Smoking Abatement System}{}{Project Lead}{January 2016 - May 2016}
\begin{itemize}
\resitem{Worked with a team of five mechanical/materials engineering students to create the bitQuit, a smart cigarette case that helps smokers control and track their cigarette use. Applying Agile development methodologies, we developed a programmable locking case that uses a BLE-enabled Arduino board to control a custom latch mechanism. Custom switches in case count cigarettes present and transmit data to bitQuit Android application via BLE. Android application presents usage data and time remaining before case unlocks.}
\end{itemize}


%-------------------------------Embedded Systems
\item
\ressubheading{Display-o-Matic e-Ink Tie}{}{Developer}{March 2016 - May 2016}
\begin{itemize}
\resitem{Developed a novelty tie prototype with built-in e-ink display. User selects image thumbnail on touchscreen linked to Gumstix Verdex board, which conveys selection to Raspberry Pi via Bluetooth. Raspberry Pi flashes new image to e-paper via GPIO pins.}
\end{itemize}

%-------------------------------High Performance
\item
\ressubheading{High Performance Fast Fourier Transform}{}{Developer}{March 2016 - May 2016}
\begin{itemize}
\resitem{Worked with two classmates to develop a set of Fast Fourier Transform implementations with varying degrees of optimization. Using a naive, serial FFT as a baseline, we applied high-performance methods (eg: code motion, blocking, loop unrolling, pThreads, OpenMP) in various combinations to maximize efficiency. Also wrote a CUDA implementation to utilize GPU parallelism.}
\end{itemize}


\end{itemize}


%######################################

\end{document}


















